---
output:
  pdf_document: default
  html_document: default
---

## **Statistical Inference: Project 2-Part 2(ToothGrowth)**

Anushri Tambe

date: "13/08/2019"
output: pdf_document

=====================================================

## Overview
In Part 2 of the course project is analyzing the ToothGrowth data in the R datasets package. Toothgrowth is a data frame with 60 observations on 3 variables.

## 1.Load the ToothGrowth data and perform some basic exploratory data analyses

```{r loading}
library(ggplot2)
library(datasets)
data(ToothGrowth)
dim(ToothGrowth)
str(ToothGrowth)
```

## 2.Provide a basic summary of the data.

```{r}
summary(ToothGrowth)
head(ToothGrowth)
ggplot(ToothGrowth,aes(x=as.factor(dose),y=len,fill=supp))+ geom_bar(stat="identity")+facet_grid(.~supp)+xlab("Dose")+       ggtitle("Effect of dose on tooth length")
dev.copy(png, file="plot.png")
dev.off()
```

## 3.Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.
Null hypothesis is there is no effect on tooth growth of different supp types
```{r}
t.test(len ~ supp, data = ToothGrowth)
```
Here pvalue is 0.06063
The confidence interval contains zero. Hence we can not reject the null hypothesis that the different supplement types have no effect on tooth length.

```{r}
doses_0.5 <- subset (ToothGrowth, dose == "0.5")
doses_1.0 <- subset (ToothGrowth, dose == "1")
doses_2.0 <- subset (ToothGrowth, dose == "2")
t.test(len ~ supp, data = doses_0.5)
t.test(len ~ supp, data = doses_1.0)
t.test(len ~ supp, data = doses_2.0)
```

## 4.Conclusion

Supplement types have no effect on tooth growth.

Inreasing dose level leads to increased tooth growth.
